Nope

### 2010-12-10 AffineLieAlgebras/MQFT2010/article.tex
Some work on BGG paper

@@

So we define new positive-definite bilinear form $(\cdot,\cdot)_+$ on the root lattice of $\gf$ by the requirement $(\delta,\delta)_+=1$. This form is only $\co{W}$-invariant. Then we define the projection $\pi_{\af}$ to the root space of the affine subalgebra $\af$ as the extension of the projection to the finite-dimensional subalgebra $\co{\af}$ with the requirement
\begin{equation}
  \label{eq:16}
  \pi_{\af}(\delta)=\delta.
\end{equation}
The orthogonality conditions in the definitions \ref{def-1}, \ref{def-2}, \ref{def-3} are to be understood with the respect to the form $(\cdot,\cdot)_+$. Then Lemma \ref{lemma-1} holds for the affine Lie algebras $\gf, \af$.
\end{enumerate}

>>>>

We consider the reduction problem for simple Lie algebra modules. We study the reduction of Verma and irreducible finite-dimensional modules of the algebra to the modules of the subalgebra. We discuss the connection of the reduction with the Bernstein-Gelfand-Gelfand resolution. We show that different structures appear in the process of reduction, for example modules of contracted algebra and generalized Verma modules from parabolic category $\mathcal{O}^{\mathfrak{p}}$.

First of all, consider the following example. 
Let Lie algebra $\gf$ be $so(5)$ and subalgebra $\af\subset \gf$ be $so(3)$. There are different embeddings of $so(3)\to so(5)$. Here we limit ourselves to the regular ones. 
The root system of the algebra $so(5)$ consists of 8 roots. We denote simple roots by $\alpha_{1}=e_{1}-e_{2}$ and $\alpha_{2}=e_{2}$, where $e_{1},e_{2}$ form standard basis. The set of the positive roots is $\Delta^{+}=\left\{\alpha_{1}, \alpha_{1}+\alpha_{2}, \alpha_{1}+2\alpha_{2}, \alpha_{2}\right\}$. Each of these roots can be taken as the simple root of the subalgebra $so(3)$. At first we consider the subalgebra $so(3)$ with the root space spanned on $\beta=\alpha_{1}+2\alpha_{2}$. Verma module $M^{\mu}$ with the highest weight $\mu=\omega_{1}+2\omega_{2}=2\alpha_{1}+3\alpha_{2}$ is shown at Figure \ref{fig:B2_Verma}.
\begin{figure}[h!bt]
  \noindent\centering{
    \includegraphics[width=120mm]{B2_Verma}
  }
  \caption{Regular embedding of $A_1$ into $B_2$. Simple roots $\alpha_1, \alpha_2$ of $B_2$ are presented as the dashed vectors.
    The simple root $\beta = \alpha_1+2\alpha_2$ of $A_1$ is indicated as the grey vector. Dimensions of weight subspaces of Verma module $M^{(1,2)}$ are shown.}

  \label{fig:B2_Verma}
\end{figure}

The branching coefficients are shown at Figure \ref{fig:B2_Verma_Branch2} for the different regular embeddings $so(3)\to so(5)$. Here we can see that the picture depends upon the embedding and looks similar to the Verma modules of some subalgebra.
\begin{figure}[h!bt]
  \noindent\centering{
    \includegraphics[width=120mm]{B2_Verma_Branch2}
  }
  \caption{Branching for the Verma modules}

  \label{fig:B2_Verma_Branch2}
\end{figure}
In present paper we interpret this branching coefficients as the dimensions of the weight subspaces of the modules of contracted algebras.

The formal character of Verma module is given by the expression
\begin{equation}
  \label{eq:17}
  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)}
\end{equation}
The denominator $R=\prod_{\alpha\in \Delta^{+}} \left(1-e^{-\alpha}\right)$ can be rewritten as the sum over the Weyl group of the algebra
\begin{equation}
  \label{eq:20}
  R=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}.
\end{equation}
Since we consider the regular embeddings, all the positive roots of the subalgebra $\af$ are in the set of positive roots of the algebra $\gf$, $\Delta^{+}_{\af}\subset \Delta^{+}$. Then we can introduce $\tilde R$ and the carrier of its expansion $\Phi$:
\begin{equation}
  \label{eq:21}
  \tilde R=\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\af}} \left( 1 - e^{-\alpha}\right)=-\sum_{\gamma\in \Phi} s(\gamma) e^{-\gamma}
\end{equation}
The ordering of roots in $\Delta _{\af}$ induce the
natural ordering of the weights in $P_{\af}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\af\subset \frak{g}}$ . The set
\begin{equation}
\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.

The root of the subalgebra is among the positive roots of the algebra. So  Verma module can be decomposed into the set of Verma modules of the subalgebra:
\begin{equation}
  \label{eq:18}
  \mathrm{ch}M^{\mu}=\sum_{\nu}b^{(\mu)}_{\nu} e^{\nu-\pi_{\af}\nu} \mathrm{ch}M^{\pi_{\af}\nu}_{\af}
\end{equation}
Using the equation \eqref{eq:21} we can write the recurrent relation for the branching coefficients $b^{(\mu)}_{\nu}$:
\begin{equation}
  \label{eq:19}
   b_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
        \delta_{\xi-\gamma_0,\mu}
        +\sum_{\gamma \in
          \Gamma _{\af \rightarrow \gf}}s\left( \gamma +\gamma _{0}\right) b_{\xi
          +\gamma }^{\left( \mu \right) }\right).
\end{equation}

@@

So we define new positive-definite bilinear form $(\cdot,\cdot)_+$ on the root lattice of $\gf$ by the requirement $(\delta,\delta)_+=1$. This form is only $\co{W}$-invariant. Then we define the projection $\pi_{\af}$ to the root space of the affine subalgebra $\af$ as the extension of the projection to the finite-dimensional subalgebra $\co{\af}$ with the requirement
\begin{equation}
  \label{eq:16}
  \pi_{\af}(\delta)=\delta.
\end{equation}
The orthogonality conditions in the definitions \ref{def-1}, \ref{def-2}, \ref{def-3} are to be understood with the respect to the form $(\cdot,\cdot)_+$. Then Lemma \ref{lemma-1} holds for the affine Lie algebras $\gf, \af$.
\item Another case that we need to consider is the of $\afb$ built on the non-simple roots.
\end{enumerate}
